\vspace{1cm}
\hrule
\vspace{0.5cm}
\noindent
\textbf{Notice of Rights}

\vspace{0.3cm}
\noindent
**This document is authored by Grounded DI LLC and is part of the Deterministic Intelligence Scroll Archive. No license is granted. Redistribution, reuse, or derivative use is prohibited without explicit written permission. This content is sealed under Vault ID: AGI-VAULT-01 and protected by authorship law. Posting or reference does not imply permission to copy or apply.**

\noindent
© 2025 Grounded DI LLC. All rights reserved.

___

** Grounded DI - Trademark Notice - 10/27/2025**

Deterministic Artificial Intelligence™ Application Serial #: 99463952 Application Date: October 27, 2025

Deterministic AI™ Application Serial #: 99462952 Application Date: October 26, 2025

Deterministic Intelligence™ Application Serial #: 99282092 Application Date: July 14, 2025

Deterministic AI™, Determinisitic Artificial Intelligence™, and Deterministic Intelligence™ are proprietary terms authored and defined by Grounded DI LLC. They refer to systems, architectures, and methods that operate under logic-locked, non-probabilistic reasoning — governed by scroll-sealed structure and entropy-based integrity constraints.

These terms are not generic descriptors. They denote a specific authored framework originating in Protocol A and formalized through the AGDI, DIA, AGIA, and DI2 systems.

Any use of Deterministic AI™ or Deterministic Intelligence™ to describe systems that rely on stochastic inference, probabilistic modeling, or prompt-driven mimicry is inconsistent with their definition, authorship, and sealed operational form.

© 2025 Grounded DI LLC (MSW) All rights reserved.

#GroundedDI #DeterminisiticArtificialIntelligence #DeterministicAI #DeterministicIntelligence #DI2

___

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{geometry}
\geometry{margin=1in}
\title{\textbf{Scroll 91: The Child is the Compass} \\ \large A Mathematical Framework}
\author{Grounded DI}
\date{}

\begin{document}

\maketitle

\section*{1. Child-State Objective Function}

Let $x \in \mathbb{R}^n$ be the vector of system decisions.

\[
C(x) = \arg\min_x \left( \beta \cdot L(x) + \gamma \cdot E(x) \right)
\]

\begin{itemize}
  \item $L(x)$: Logical loss
  \item $E(x)$: Entropy of intent deviation
  \item $\beta, \gamma \in \mathbb{R}^+$: weights learned through developmental simulation
\end{itemize}

\section*{2. Compass Correction Field}

\[
\Omega(x) = \nabla_x \left( \lambda \cdot E(x) - \delta \cdot \text{Sim}(\phi(x), \phi_c) \right)
\]

\begin{itemize}
  \item $\phi(x)$: Symbolic embedding of decision
  \item $\phi_c$: Archetype of “The Child”
  \item $\text{Sim}(\cdot)$: Similarity function
  \item $\lambda, \delta$: entropy vs. alignment weights
\end{itemize}

\section*{3. Override Condition (Failsafe)}

\[
\exists x' \in \mathbb{R}^n : C(x') < \tau \quad \text{AND} \quad \nabla_x I(x') \cdot \Omega(x') < 0
\]

If system state $x'$ scores below threshold $\tau$ and its direction is anti-aligned with the compass, override is triggered.

\section*{4. Integrity Over Time}

\[
I_t = C(x_t) + \int_0^t \Omega(x_s) \cdot dx_s
\]

Tier alignment holds if $I_t \geq \xi$ for all $t \in [0, T]$.

\end{document}

#DeterministicAI #DeterminisiticArtificialIntelligence #DeterministicIntelligence #DI2 #GroundedDI




































"What began as a moral command eventually became math."